Variation in distance between consecutive animal locations

### 2021-03-15 distributions_paper/rudolph_distributions_testing.Rmd
Playing with the other focus variables

# focus <- "dist"
# focus <- "R2n"
 focus <- "mpm"
# focus <- "m15"

if(focus == "dist"){
  df <- aracari_df %>%
  dplyr::filter(dist != 0) %>%
  group_by(id) %>%
  filter(., n() >= 30) %>%
  ungroup() %>%
  dplyr::filter(dist != 0) %>% 
    mutate(Bird_ID = paste0("B", id),
           focus = dist)

  dist.used <- c("lnorm", "weibull", "cauchy")
  param <- c("meanlog", "sdlog", "shape", "scale", "location", "scale")
  dist <- c("lnorm", "lnorm", "weibull", "weibull", "cauchy", "cauchy")
  kpars <- c(2, 2, 2, 2, 2, 2)
}

@@

pop <- lapply(dist.used, function(x){fitdist(df$focus, distr = x)})

@@

  fit <- lapply(dist.used, function(x){fitdist(fit.df$focus, distr = x)})

@@

prms.df %>% 
  mutate(param = str_to_upper(param), 
         dist = str_replace(dist, "exp", "Exponential"),
         dist = str_replace(dist, "gamma", "Gamma"),
         dist = str_replace(dist, "weibull", "Weibull"),
         dist = str_replace(dist, "lnorm", "Lognormal"),
         data = str_replace(data, "pop", "POP")) %>% 
  mutate(BIC = log(n)*kpars - 2*loglik,
         AIC = 2*kpars - 2*loglik,
         AICc = AIC + (2* kpars * (kpars+1)/(n-kpars-1))) %>% 
  group_by(data) %>% 
  mutate(deltaBIC = signif(BIC - min(BIC), 3),
         deltaAIC = signif(AIC - min(AIC), 3),
         deltaAICc = signif(AICc - min(AICc), 3)) %>% 
  mutate(best_bic = ifelse(deltaBIC == 0, "#ffaa00", "black"),
         best_aic = ifelse(deltaAIC == 0, "#fc0362", "black")) -> nice_prms
```

@@

```{r fig.height=10, fig.width=12}

>>>>

# focus <- "dist"
# focus <- "R2n"
# focus <- "mpm"
# focus <- "m15"

if(focus == "dist"){
  df <- aracari_df %>%
  dplyr::filter(dist != 0) %>%
  group_by(id) %>%
  filter(., n() >= 30) %>%
  ungroup() %>%
  dplyr::filter(dist != 0) %>% 
    mutate(Bird_ID = paste0("B", id),
           focus = dist)
  dlevy <- function(x, m, s) sqrt(s/(2*pi*(x-m)^3))*exp(-s/(2*(x-m)))
  plevy <- function(q, m, s) 2*(1-pnorm(1/sqrt((q-m)/s)))
  qlevy <- function(p, m, s) s/qnorm(1-p/2)^2+m
  rlevy <- function(n, m, s) s/qnorm(1-runif(n)/2)^2+m
  fitlevy <- fitdist(df$dist, "levy", start=list(m=0, s=0.5))

  dist.used <- c("lnorm", "weibull", "cauchy", "levy")
  param <- c("meanlog", "sdlog", "shape", "scale", "location", "scale", "location" , "scale")
  dist <- c("lnorm", "lnorm", "weibull", "weibull", "cauchy", "cauchy", "levy", "levy")
  kpars <- c(2, 2, 2, 2, 2, 2, 2, 2)
}

@@

pop <- lapply(dist.used, function(x){
  if(x == "levy"){
    fitdist(df$focus, "levy", start=list(m=0, s=0.5))
  }
  else{
    fitdist(df$focus, distr = x)
  }
})

@@

  #fit <- lapply(dist.used, function(x){fitdist(fit.df$focus, distr = x)})

  fit <- lapply(dist.used, function(x){
  if(x == "levy"){
    fitdist(fit.df$focus, "levy", start=list(m=0, s=0.5))
  }
  else{
    fitdist(fit.df$focus, distr = x)
  }
})

@@

prms.df %>% 
  mutate(param = str_to_upper(param), 
         dist = str_replace(dist, "exp", "Exponential"),
         dist = str_replace(dist, "gamma", "Gamma"),
         dist = str_replace(dist, "weibull", "Weibull"),
         dist = str_replace(dist, "lnorm", "Lognormal"),
         dist = str_replace(dist, "levy", "Levy"),
         data = str_replace(data, "pop", "POP")) %>% 
  mutate(BIC = log(n)*kpars - 2*loglik,
         AIC = 2*kpars - 2*loglik,
         AICc = AIC + (2* kpars * (kpars+1)/(n-kpars-1))) %>% 
  group_by(data) %>% 
  mutate(deltaBIC = signif(BIC - min(BIC), 3),
         deltaAIC = signif(AIC - min(AIC), 3),
         deltaAICc = signif(AICc - min(AICc), 3)) %>% 
  mutate(best_bic = ifelse(deltaBIC == 0, "#ffaa00", "black"),
         best_aic = ifelse(deltaAIC == 0, "#fc0362", "black")) -> nice_prms
```

@@

```{r eval=FALSE, fig.height=10, fig.width=12}
